Brownian Dynein Model

### 2015-07-22 latex/derivation.tex
convert equations to align

\section{Cartesian from Angular Coordinates}
$$X_{bl}$$
$$X_{ml} = X_{bl}+L_{t}\cos(\Theta_{bl})$$
$$X_{t}  = X_{ml}+L_{s}\cos(\Theta_{ml})$$
$$X_{mr} = X_{t} +L_{s}\cos(\Theta_{mr}-\pi)$$
$$X_{br} = X_{mr}+L_{t}\cos(\Theta_{br}-\pi)$$

>>>>

\section{Cartesian from Angular Coordinates}
\begin{align}
  X_{bl} &= 0 \\
  X_{ml} &= X_{bl}+L_{t}\cos(\Theta_{bl}) \\
  X_{t}  &= X_{ml}+L_{s}\cos(\Theta_{ml}) \\
  X_{mr} &= X_{t} +L_{s}\cos(\Theta_{mr}-\pi) \\
  X_{br} &= X_{mr}+L_{t}\cos(\Theta_{br}-\pi) \label{eq:br-definition}
\end{align}

As we found in Eq.~\ref{eq:br-definition}... just kidding!
